---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pkgpins

<!-- badges: start -->
[![R-CMD-check](https://github.com/ijlyttle/pkgpins/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ijlyttle/pkgpins/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of pkgpins is to show how to serve a dataset using [pins](https://pins.rstudio.com/) and [pkgdown](https://pkgdown.r-lib.org/).

## Installation

You can install the development version of pkgpins from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ijlyttle/pkgpins")
```

That said, you almost assuredly don't want to install this package.

## Example

This package contains exactly one thing: a shamelessly unoriginal dataset, where a column is added for metric consumption.

```{r example}
library("pkgpins")

head(mtcars_metric)
```

The purpose of this package is to demonstrate that a package dataset can be published and consumed using pins and pkgdown.


